---
title: Data Synth
author: Dominic Pearce
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, fig.align = 'center')
```

```{r}
library(tidyverse)
library(ggthemes)
source("../lib/models_R.r")
```


### Age

#### So we'll want to divide our age demographic into male and female. Then we just say that the distribution is largely a couple of normal distributions spanning an age range next to one another as from [this website](http://www.gov.scot/Topics/People/Equality/Equalities/DataGrid/Age/AgePopMig)

#### *edit:* actually, male and female age distributions are pretty much identical so we can consider them as a single group

```{r}
simAge <- function(n, sd = 12){
    age_ranges <- list(16:40, 41:90)
    age_vec <- sapply(age_ranges, function(x) rnorm(n, mean = mean(x), sd = sd)) %>% 
        c() %>%
        round()
    age_vec[age_vec < 16 | age_vec > 90] <- NA
    limits_vec <- as.vector(na.omit(age_vec))
    sample(limits_vec, 1000)
}
```

### Place of Birth

#### We'll use a table from [council area population estimates](https://en.wikipedia.org/wiki/Demography_of_Scotland#Place_of_birth) from wikipedia

```{r}
simArea <- function(n){
    cpop_dfr <- read.csv("../data/council-population.csv")
    total_2011 <- sum(cpop_dfr$n_2011)
    sample(cpop_dfr$local_council_area, 1000, replace = TRUE, prob = cpop_dfr$n_2011)
}
```

### Alcohol use

#### This will need to be divided by gender.

```{r}
alc_dfr <- read.csv("../data/alcohol.csv")

simBinge <- function(age, sex){
    prop = alc_dfr$prop[alc_dfr$age == age & alc_dfr$sex == gender]
    sample(c(TRUE, FALSE), 1, prob = c(prop, 100-prop))
}



```

### Physical Activity

#### Using percentages from the Chief Medical Officer

```{r}
simActivity <- function(n){
sample(c("low", "mid", "high"), n, replace = TRUE, prob = c(25.6, 13.7, 60.7))
}
```


### Build the dataset


```{r}
set.seed(123)
sim_dfr <- data.frame(
                      age = simAge(1000),
                      gender = sample(c("MALE", "FEMALE"), 1000, replace = TRUE),
                      area = simArea(1000), 
                      activity = simActivity(1000)
                      )
add_dfr <- lapply(1:nrow(sim_dfr), function(x){
                            sub_dfr <- sim_dfr[x,]
                            age <- sub_dfr$age
                            gender <- as.character(sub_dfr$gender)
                            data.frame(binge = simBinge(age, gender), 
                                       stroke = predict_stroke(age, gender),
                                       diabetes = predict_diabetes(age, gender),
                                       cancer = predict_cancer(age, gender),
                                       bmi = predict_bmi(age, gender)
                                       )
                      }) %>% do.call(rbind, .)
sim_dfr <- cbind(sim_dfr, add_dfr)


ggplot(sim_dfr, aes(x = age, fill = gender)) +
    geom_density(alpha = 0.5) +
    theme_pander()

ggplot(sim_dfr, aes(x = area)) + 
    geom_histogram(stat = 'count') + 
    theme_pander() + 
    theme(axis.text.x = element_text(angle = 90)) 

ggplot(sim_dfr, aes(x = area, fill = activity)) + 
    geom_bar(stat = 'count', position = 'dodge') + 
    theme_pander() + 
    theme(axis.text.x = element_text(angle = 90))

ggplot(sim_dfr, aes(x = diabetes, y = bmi)) + geom_point() + geom_smooth(method = 'lm')
```
